Neuroecon Poster Figures

### 2017-10-04 code/NeuroeconPoster.Rmd
finished first draft

```{r}
tmp %>%
  filter(ddm_task == 1) %>%

@@

```{r}

@@

```{r}

>>>>

p8 = measure_labels %>%
  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == "task") %>%
  select(-var, -task) %>%
  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
  filter(ddm_task == 1) %>%
  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
  na.omit() %>%
  ggplot(aes(icc))+
  geom_histogram(aes(fill=param),  alpha=0.5, position = 'identity')+
  facet_wrap(~raw_EZ_hddm)+
  theme_bw()+
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.text= element_text(size=30),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=20),
        axis.title.x = element_text(size = 30),
        axis.title.y = element_text(size = 30),
        strip.text = element_text(size=30))

ggsave('DDM_raw_comp_Poster.jpg', plot = p8, device = "jpeg", path = "../output/figures/", width = 18, height = 5, units = "in")
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == "task") %>%
  select(-var, -task) %>%
  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
  filter(ddm_task == 1) %>%
  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
  na.omit()

summary(lm(icc~raw_EZ_hddm, data=tmp[tmp$raw_EZ_hddm != "raw",]))
```

```{r}
summary(lm(icc~raw_EZ_hddm, data=tmp[tmp$raw_EZ_hddm != "EZ",]))
```

```{r}
summary(lm(icc~raw_EZ_hddm, data=tmp[tmp$raw_EZ_hddm != "hddm",]))
```

@@

```{r}
p9 = rel_df %>%
  ggplot(aes(icc, spearman, color=task))+
  geom_point()+
  geom_abline(intercept = 0, slope=1))+
  theme_bw()+
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.text= element_text(size=30),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=20),
        axis.title.x = element_text(size = 30),
        axis.title.y = element_text(size = 30),
        strip.text = element_text(size=30))

ggsave('ICC_Spearman_Poster.jpg', plot = p9, device = "jpeg", path = "../output/figures/", width = 10, height = 10, units = "in")
```
